---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  cache = TRUE,
  out.width = "100%"
)
```

# pdfcolorsplit

<!-- badges: start -->
<!-- badges: end -->

{pdfcolorsplit} is an utility to split a PDF file into a file containing color sheets, and a file containing B&W sheets.

This is useful when one must print a document, but the printer does not automatically choose the ink based on the content.

## Features

- Color detection using {[magick](https://cran.r-project.org/web/packages/magick/index.html)}
- Can deal with single- and double-sided PDFs

## Installation

The package is not in CRAN yet.  
You can simply install it from this repository:

```{r, eval=FALSE}
remotes::install_github("lgaborini/pdfcolorsplit")
```

## Example

Let's prepare the [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/) for printing!

```{r, include=FALSE}
devtools::load_all(".")
```


```{r tidy-pdf, cache=TRUE, eval=-1}
library(pdfcolorsplit)

f_pdf_local <- "assets/rmarkdown-cookbook.pdf"

df_pages <- tidy_pdf_pages(
   pdf = f_pdf_local,
   double_sided = TRUE
)
```

How many pages must be printed in color?

```{r}
df_pages %>% 
   dplyr::count(is_color_page)
```

How many SHEETS must be printed in color? (this is the actual printing cost)

```{r}
df_pages %>% 
   dplyr::count(is_color_sheet)
```

Show one random color page:

```{r img-sample}
df_pages %>% 
   dplyr::filter(is_color_page) %>% 
   dplyr::slice_head(n = 1) %>% 
   dplyr::pull(img)
```

Split in two parts:

```{r, eval=FALSE}

# The directory that will contain the files
output_dir <- tempdir()

df_pages %>% 
   split_pdf_chunks(
      pdf = f_pdf_local,
      output_dir = output_dir
   )

```



